
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Harry Angelo Soer} \\ \vspace{1pt}
    \small +63 977 390 2303 $|$ \href{mailto:gelo.soer@gmail.com}{\underline{gelo.soer@gmail.com}} $|$ 
    \href{https://linkedin.com/in/harry-angelo-soer}{\underline{linkedin.com/in/harry-angelo-soer}} \\
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Philippine Christian University}{2013 -- 2017}
      {Bachelor of Science in Information Technology}{Manila City, Philippines}
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {AppEvolve}{Nov 2022 -- Present}
      {Senior Frontend Developer}{Philippines}
      \resumeItemListStart
        \resumeItem {Led the frontend development team, overseeing UI integration across web and mobile platforms.}
        \resumeItem {Contributed to the integration of agentic AI-driven development workflows using Cursor and ClaudeCode.}
        \resumeItem {Implemented analytics solutions to support data-driven business and product decisions.}
        \resumeItem {Collaborated closely with backend engineers to optimize and streamline API integrations.}
        \resumeItem {Built React Native applications featuring real-time location tracking and push notifications using Firebase or Expo Push Notifications.}
      \resumeItemListEnd

    \resumeSubheading
      {LUXCLUSIF}{May 2021 -- Jan 2023}
      {Software Engineer}{Manila, Philippines}
      \resumeItemListStart
        \resumeItem{Contributed to R\&D efforts for internal business applications.}
        \resumeItem{Used JavaScript, TypeScript, ReactJS, MaterialUI, NodeJS, SQL, REST APIs, Application Insights.}
      \resumeItemListEnd

    \resumeSubheading
      {High Output Ventures}{Jan 2020 -- May 2021}
      {Frontend Web Developer}{Singapore}
      \resumeItemListStart
        \resumeItem{Developed frontend features using ReactJS, NextJS, Redux, Zustand, GraphQL, Framer Motion.}
        \resumeItem{Collaborated via Figma and shipped to projects: \texttt{hov.co}, \texttt{her.vn}.}
      \resumeItemListEnd

    \resumeSubheading
      {Creatella}{Feb 2019 -- Jan 2020}
      {Frontend Developer}{Philippines}
      \resumeItemListStart
        \resumeItem{Maintained and developed ReactJS/React Native applications.}
        \resumeItem{Projects: Yoripe App, My Development Space.}
      \resumeItemListEnd

    \resumeSubheading
      {Racket Studios}{Jun 2018 -- Mar 2019}
      {Part-time Frontend Developer}{Philippines}
      \resumeItemListStart
        \resumeItem{Built web and desktop apps using Angular, Electron, TypeScript, MongoDB.}
        \resumeItem{Project: \texttt{racketstudios.com/demo}.}
      \resumeItemListEnd

    \resumeSubheading
      {VOLENDAY}{Oct 2017 -- Feb 2019}
      {Web Developer}{Makati City, Philippines}
      \resumeItemListStart
        \resumeItem{Worked with MongoDB, ExpressJS, ReactJS, SASS, NodeJS.}
        \resumeItem{Projects: asia-ceo.org, damaslatinasmanila.org, bonaevents.com, On the Field App.}
      \resumeItemListEnd

    \resumeSubheading
      {8Layer Technologies, Inc.}{Apr 2016 -- Aug 2016}
      {Intern}{Philippines}
      \resumeItemListStart
        \resumeItem{Used Laravel, MySQL, Git, and Docker for full-stack development.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects Contributed}
  \resumeSubHeadingListStart
    \resumeItem{Yoripe App - \href{https://play.google.com/store/apps/details?id=com.yoripeapp}{play.google.com/store/apps/details?id=com.yoripeapp}}
    \resumeItem{My Development Space - \href{https://mydevelopmentspace.com/}{mydevelopmentspace.com}}
    \resumeItem{Asia CEO - \href{https://www.asia-ceo.org/}{asia-ceo.org}}
    \resumeItem{Damas Latinas Manila - \href{http://www.damaslatinasmanila.org/}{damaslatinasmanila.org}}
    \resumeItem{Bona Events - \href{https://www.bonaevents.com/}{bonaevents.com}}
    \resumeItem{StaffWerk - \href{googleplay}{https://play.google.com/store/apps/details?id=com.staffwerk.app} \href{appstore}{https://apps.apple.com/us/app/staffwerk/id1527734882}}
    \resumeItem{VinDrives - \href{https://vindrives.app/}{https://vindrives.app/}}
    \resumeItem{BrainTrust - \href{https://www.usebraintrust.com/}{https://www.usebraintrust.com/}}
  \resumeSubHeadingListEnd

\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeItem{
      \textbf{Languages}{: JavaScript, TypeScript, ES6, Python, HTML, CSS, SQL} \\
      \textbf{Frameworks/Libraries}{: ReactJS, React Native, NextJS, NodeJS, Django, Redux, Zustand, GraphQL, Material UI, Framer Motion, Angular, SASS, TailwindCSS} \\
      \textbf{Tools}{: Git, Docker, Firebase, Electron, Figma, Application Insights, Cursor IDE, VSCode with Claude Code} \\
      \textbf{Backend/Database}{: REST APIs, MongoDB, MySQL, PostgresSQL, NodeJS, Django} \\
    }
  \resumeSubHeadingListEnd

\end{document}
